### 2016-11-03 paper/intro.tex
quick pass in text

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  It analyzes, for
each test, which file dependencies have been change impacted.

@@

Motivated by this potential gap in regression testing practice, this
paper studies (1) how prevalent long-running test suites are in
open-source software projects.  To conduct this experiment we selected
\numSubjs{} Java projects from github that are highly-popular and use
the Maven build system.  (Section~\ref{sec:eval} details our selection
criteria.)  Our experimental results indicate that long-running test
suites (taking longer than 5m\Fix{check if Ekstazi paper also used
  this value and cite} to complete) are not rare (\Fix{17\%} of the
projects).  From this result we investigated (2) how frequently
long-running test suites use parallelization.  Our results indicate
that \Fix{80\%} of the long-running projects do use parallelization to
speedup execution.  Given the popularity of this solution, we further
studied: (3) what are the causes of high execution cost in individual
tests (CPU vs. IO) and (4) how uniformly cost is distributed across
tests.  These questions help to assess the impact of parallelization
in each of these projects.  Intuitively, IO-intensive test suites and
test suites with uneven distribution of cost per test are factors that
limit the effects of parallelization.  Results indicate that \Fix{...}
Finally, we investigated (5) what are the limitations related with
parallelization that could justify adoption resistance.

>>>>

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  To that end
Ekstazi analyzes, for each test, which test-dependent files have
changed.

@@

Motivated by this potential gap in regression testing practice, we
first studied (1) how prevalent long-running test suites are in
open-source software projects.  To conduct this experiment we selected
\numSubjs{} Java projects from github that are highly-popular and use
the Maven build system.  (Section~\ref{sec:eval} details our selection
criteria.)  Our experimental results indicate that long-running test
suites (taking longer than 5m\Fix{check if Ekstazi paper also used
  this value and cite} to complete) are not rare~--~\Fix{17\%} of the
projects we analyzed contain long-running test suites.  From this
result we investigated (2) how frequently long-running test suites use
parallelization\Mar{justify why parallelization}.  Our results
indicate that \Fix{80\%} of the long-running test suites do use
parallelization to speedup execution.  Given the popularity of this
solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in each of these projects.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the effects of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related with parallelization that could justify
adoption resistance.

### 2016-11-03 paper/modes.tex
quick pass in text

\section{Modes of Parallel Execution}

%%, potentially using commodity hardware

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates some of these levels.  This paper
focuses at lower-level parallelism, obtained with parallel computation
at cpus and threads in a given machine.  This kind of parallelism is
enabled through build systems and testing frameworks.  Given the
proliferation of multicore machines it is not surprising that testing
frameworks provide today support for parallel test execution with the
goal of running tests more efficiently~\cite{junit-org,testng,nunit}.
Build systems wrap the features of these frameworks to facilitate the
use of such technology\cite{maven-surefire-plugin}.  In the following
we elaborate relevant features of these components focusing on Java,
Maven, and JUnit but the discussion can be generalized to other
languages, build systems, and testing frameworks.

>>>>

\section{Parallel Execution of Test Suites}

\Mar{add a sentence to introduce this section at a higher abstraction
  level.}  Parallelism in test execution can be obtained at different
levels.  Figure~\ref{fig:levels} illustrates some of these levels.

This paper focuses at lower-level parallelism, obtained with parallel
computation at cpus and threads in a given machine.  This kind of
parallelism is enabled through build systems and testing frameworks.
Given the proliferation of multicore machines it is not surprising
that testing frameworks provide today support for parallel test
execution with the goal of running tests more
efficiently~\cite{junit-org,testng,nunit}.  Build systems wrap
parallel features offered by testing frameworks to facilitate the use
of such technology\cite{maven-surefire-plugin}.  In the following we
elaborate relevant features of these components focusing on Java,
Maven, and JUnit but the discussion can be generalized to other
languages, build systems, and testing frameworks.
